\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}

% extra packages
\usepackage{amsmath, amssymb}

\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}
\usepackage{footmisc}
\usepackage{url}

%\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
\Large \textbf{List of Publications}

\Large Youngmin Park
\end{center}

\begin{enumerate}
\item \textbf{Park, Y.}, Wilson, D. ``High-Order Accuracy Computation of Coupling Functions for Strongly Coupled Oscillators.'' SIAM Journal on Applied Dynamical Systems 20.3:1464--1484 (2021).
 \item \textbf{Park, Y.}, Fai, T.G. ``The Dynamics of Vesicles Driven Into Closed Constrictions by Molecular Motors.'' Bulletin of Mathematical Biology. 82.141 (2020).
 \item \textbf{Park, Y.}, Geffen, M.N. ``A Circuit Model of Auditory Cortex.'' PLOS Computational Biology. 17.6:e1008016
 (2020).
 \item Ermentrout, G.B., \textbf{Park, Y.}, Wilson, D. ``Recent advances in coupled oscillator theory.'' Philosophical Transactions A. 377. (2019).
 \item \textbf{Park, Y.}, Ermentrout, G.B. ``A Multiple Timescales Approach to Bridging Spiking- and Population-level Dynamics.'' Chaos 28.8:083123 (2018).
 \item \textbf{Park, Y.}, Ermentrout, G.B. ``Scalar Reduction of a Neural Field Model with Spike Frequency Adaptation.'' SIAM Journal on Applied Dynamical Systems 17.1:931--981 (2018).
 \item \textbf{Park, Y.}, Shaw, K.M. Chiel, H.J. Thomas, P.J. ``The Infinitesimal Phase Response Curve of Oscillators in Piecewise Smooth Dynamical Systems.'' European Journal of Applied Mathematics 29.5:905--940 (2018).
 \item \textbf{Park, Y.}, Ermentrout, G.B. ``Weakly Coupled Oscillators in a Slowly Varying World.'' Springer Journal of Computational Neuroscience 40.3:269--281 (2016).
 \item Shaw, K.M., \textbf{Park, Y-M.}, Chiel, H.J., Thomas, P.J. ``Phase Resetting in an Asymptotically Phaseless System: On the Phase Response of Limit Cycles Verging on a Heteroclinic Orbit." SIAM Journal on Applied Dynamical Systems 11.1:350--91 (2012).
\end{enumerate}

\textbf{Recently submitted:}
\begin{enumerate}
	\item \textbf{Park, Y.}, Fai, T.G. ``Coarse-grained Stochastic Model of Myosin-Driven Vesicles into Dendritic Spines''
	\item Fai, T.G., \textbf{Park, Y.} ``Global Asymptotic Stability of an Active  Disassembly Model of Flagellar Length Control.''  \url{https://arxiv.org/abs/2010.08163}.
\end{enumerate}


\end{document}