\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}

% extra packages
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}

%\setlength{\parindent}{0pt}

\signature{Youngmin Park}
\address{3729 Spring Garden St. \\ Philadelphia \\ PA 19104}

\begin{document}
\begin{letter}{Youngmin Park \\ Department of Otorhinolaryngology\\ University of Pennsylvania}
 

\opening{To Whom it may concern:}

My name is Youngmin Park. I hold a PhD in mathematics from the University of Pittsburgh with advisor G. Bard Ermentrout. My work is largely in the realm of smooth and non-smooth dynamical systems with a strong emphasis on neuroscience-motivated problems.

My recent work involves the reduction of high dimensional conductance-based or mean-field models to low dimensional scalar models amenable to a classic, straightforward dynamical systems analysis. Moreover, in a recent publication with my masters advisor (Peter J. Thomas) and colleagues, we derive a solution to jump discontinuities in the phase response curve of piecewise smooth oscillators.

At the moment, I am a postdoctoral researcher at the University of Pennsylvania department of Otorhinolaryngology, working in computational neuroscience with Maria N. Geffen. While my brief stay in her lab has been a deeply enriching and educational experience, my long-term career goals have ended up at odds with the goals of the lab.

With my application, I include a curriculum vitae (which includes a list of publications and teaching experience).

Please let me know if there is anything else I can provide. Thank you in advance for your consideration.

Sincerely,
Youngmin Park
 
 
 
\end{letter}
\end{document}
