\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{longtable}
% extra packages
\usepackage[top=1in, left=1in, right=1in, bottom=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}

%\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
\Large \textbf{Diversity Statement}

\Large Youngmin Park
\end{center}

I am a first-generation native South Korean who grew up all over the world (including Swaziland, South Korea, and the Philippines), but by and large grew up in poverty in the United States. These environments exposed me to diverse cultures (including severe socio-economic disparities), and I learned to adapt to many types of foreign etiquette at an early age. While I have lived in the US since adolescence, this country is incredibly unique and I have continuously adjusted over the past several decades to fit into its culture. This experience, combined with my close friendships with people of diverse backgrounds, has helped me understand the difficulty of adjusting to a new life in the US while attending a competitive program. We must actively help students who struggle in this way for the good of the nation's economy and security \cite{jones2018call}.

While growing up, I made many friends with people with vastly different socio-economic and cultural backgrounds. Looking back, it is especially striking that none of my friends from poor families earned a college degree, even though they are all incredibly intelligent. Those of us who went to the same well-funded high school took very different paths, and it is not simply an issue of interest. They are brilliant people who would have thrived in college and could have greatly advanced their careers on the newfound connections. People who could have advanced to positions with greater sway over greater numbers of people, allowing them to guide policies and make decisions benefiting their community, and eventually, their city, state, and country. The world pushed them away from their full potential, and this realization is painful. Indeed, my anecdotal experience aligns with known demographic differences \cite{jones2018call} due to a lack of student engagement \cite{kokkelenberg2010succeeds,savaria2017critical}.

I have taken steps to fight against this unfairness for future generations. From the moment I started teaching at U Pitt, my attempts at fostering diversity, equity, and inclusion have been implicit but powerful. My teaching style takes elements from expeditionary learning, inquiry-based learning, and differentiated instruction. The active component of my teaching is important because it has been shown to improve student performance in underrepresented groups in STEM \cite{theobald2020active}, while differentiated instruction allows me to tailor my teaching to the individual.
%Many faculty have given strong advice on effective teaching, but most notably Fern Hunt, an established and strong mathematician who went to graduate school during a time of segregation, generously set aside a few hours to advise me on how to interact with people of different backgrounds. She suggested I read books on the history of different cultures, and most importantly, to try to see the person's \textit{soul} as opposed to a collection assumptions. I have taken this suggestion to heart and have started reading \textit{One Hundred Years of Solitude} and \textit{The Rape of Nanking}. I will transition to biographies of famous Americans of various cultural backgrounds.

My teaching style has always been driven by this principle of viewing students as individuals and not just as a classroom. My teaching efforts are always \textbf{independent of a student's race, gender, or socio-economic background}. I hope to see a world where every student has access to teachers who genuinely want their students learn and succeed, based on the tenets of \textbf{diversity, equity, and inclusion}. To this end I have taught as a guest lecturer in science for underrepresented Bangladeshi children at Moder Patshala and the Free Library of Pennsylvania. At Brandeis, I volunteered in science outreach to give neuroscience lectures at Waltham High School (the series was canceled due to COVID-19).

UCLA hosts an unusually comprehensive set of tools, including a wonderfully comprehensive EDI syllabus for faculty. I wish to participate in the numerous training opportunities, including \textbf{UCLA LGBTQ Ally training}, \textbf{Title IX Events and Workshops}, and \textbf{Intergroup Dialogue Peer Facilitator Training}. While I am careful with regards to diversity, it is not possible for me to expose my hidden biases that could negatively affect my day-to-day interaction with others. It is only through discussion and training that I can identify and overcome my shortcomings I would be honored to be a part of an environment that values diversity to this degree.

%In the future, I will continue to seek opportunities in science outreach and join organizations advocating for underrepresented groups, including the Society for Advancement of Chicanos/Hispanics and Native Americans in Science (SACNAS), and the Association for Women in Mathematics (AWM). \textbf{All people deserve the best from their teachers and I will not stop working to make this hope a reality}.


%Racism causes results in preconceived notions formed by exaggerated circumstances such as those that occur in popular media. Every day I work to understand that each individual I meet is no more than my interactions with them, and that I should form my own opinions based on our mutual experiences. This philosophy naturally transfers to my teaching, where I evaluate a student's needs based directly on my interactions with them, as opposed to what I have experienced with people of a similar socio-economic status. It is a lifelong challenge that I wholeheartedly accept. Some students require more mentoring, while others recognize patterns very quickly. \textit{By adjusting my teaching based on the individual, I become a maximally effective teacher}. I help all of my students to the best of my abilities regardless of race, gender, background, and disability.
\newpage
\bibliographystyle{plain}
\bibliography{edi}
\end{document}
