\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}

% extra packages
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}

%\setlength{\parindent}{0pt}

\signature{Youngmin Park}
\address{936 Lilac St. \\ Pittsburgh \\ PA 15213}

\begin{document}
\begin{letter}{Youngmin Park \\ Department of Mathematics\\ University of Pittsburgh}
 

\opening{Dear Dr. Jonathan Touboul:}

My name is Youngmin Park. I am a graduate student at the University of Pittsburgh department of mathematics, working in the areas of weakly coupled oscillators and neural field models. I expect to receive a Ph.D. from the University of Pittsburgh in May of 2018 under the direction of my advsior Bard Ermentrout. I would like to apply for a postdoctoral position in your group.

I work in dynamical systems with a strong emphasis on neuroscience-motivated problems. My masters thesis is on the phase response curve of piecewise smooth oscillators, which is useful for studying entrainment in piecewise smooth neural models. It is a topic which I continue to pursue today. Other recent work involves the reduction of high dimensional conductance-based neural models or mean-field neural models to low dimensional scalar models.

My professional goals are primarily academic and research-oriented. Following a successful postdoc, I plan to apply for tenure-track jobs in applied mathematics or computational biology. The ultimate goal is to continue producing results in mathematical neuroscience and to form strong collaborations with experimental groups to form new theoretical problems.

With my application, I include a curriculum vitae (which includes a list of publications and links to source code).

Please let me know if there is anything else I can provide. Thank you in advance for your consideration.

Sincerely,
Youngmin Park
 
 
 
\end{letter}
\end{document}
