%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%------RMIT Letterhead------------%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper]{letter}

%\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
%\usepackage[utf8]{inputenc}

%\usepackage[T1]{fontenc}

% you may specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc.)
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{gfsdidot}
\usepackage[T1]{fontenc}

\input{head.tex}

\begin{document}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------
\def\School{Brandeis University}
\begin{letter}
{Hiring Committee\\
Department of Mathematics, MS 050\\
Brandeis University\\
415 South Street\\
Waltham, MA 02453}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Members of the Hiring Committee,}

I am applying for the position of Tenure-Track Assistant Professor in Mathematics at \School. I hold a Ph.D. in mathematics from the University of Pittsburgh advised by G. Bard Ermentrout, and now hold a postdoctoral position at Brandeis University advised by Thomas G. Fai. I specialize in \textbf{deterministic and stochastic dynamical systems}, \textbf{bifurcation theory}, \textbf{perturbation methods}, and \textbf{non-local integro-differential equations}, with applications to chemistry, neuroscience, and cell physiology.

My doctoral research in dimension reduction resulted in winning the prestigious \textbf{Andrew Mellon Predoctoral Fellowship}, awarded to doctoral students of exceptional promise and ability. I was the first math-bio doctoral student at the University of Pittsburgh to receive this award. My research ability has matured through my postdocs: at the University of Pennsylvania, I collaborated closely with neuroscientists and published ground-breaking models to explain data produced by the world's leading auditory labs. At Brandeis, I have continued to develop my ability as an independent mathematician while publishing and collaborating in multiple fields, including coupled oscillators, molecular motor dynamics, and chemical networks.

\School~features strong researchers in mathematical biology, including \textbf{Thomas Fai} and \textbf{Jonathan Touboul}. My research experience in molecular motor transport and mathematical neuroscience will augment their work through collaborations and grants, and I will enhance the department's reputation through my independent research program. I use dynamical systems and bifurcation theory to solve problems of oscillator synchrony in chemical and biological networks and use machine learning to uncover network properties in biological systems.

I am also committed to providing high-quality and equal education for all my students, as evidenced by my teaching evaluations. My teaching portfolio boasts eight years of teaching at different capacities (lectures, recitations, grading), at different levels (calculus sequence, differential equations, linear algebra, and discrete math), and at different institutions (Oberlin College, Case Western Reserve University, University of Pittsburgh, and Brandeis University). As a doctoral student, my students shortlisted me for the \textbf{Elizabeth Baranger teaching award}, the most prestigious teaching award at the University of Pittsburgh. In terms of outreach, I have served as a guest lecturer for underprivileged Bangladeshi children at the Free Library of Philadelphia, and will serve as a a guest lecturer in science at Waltham High School.

%I strongly believe in the principle that learning is best accomplished with context and practice. My students do not learn in a vacuum, but instead learn concepts alongside the human triumph and defeat behind many concepts we take for granted today, such as matrix notation and Euclid's fifth postulate. Students at \School~will greatly benefit from this approach, and in turn, will drive me towards excellent instruction.

As part of my application I include a curriculum vitae, research statement, and teaching statement. Please request additional details as needed, and I look forward to our correspondence.

\closing{Sincerely,}
%----------------------------------------------------------------------------------------
\end{letter}
\end{document}