%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%------RMIT Letterhead------------%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper]{letter}

%\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
%\usepackage[utf8]{inputenc}

%\usepackage[T1]{fontenc}

% you may specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc.)
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{gfsdidot}
\usepackage[T1]{fontenc}

\input{head.tex}

\begin{document}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------

\def\School{Simpson College}

\begin{letter}
{Search Committee\\
Mathematics Department\\
701 N C Street\\
Indianola IA 50125}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Members of the Search Committee,}


I am applying for the position of Assistant Professor at the \School~Department of Mathematics. \input{intro0_dyn}

My doctoral research in dimension reduction resulted in winning the prestigious \textbf{Andrew Mellon Predoctoral Fellowship}, awarded to doctoral students of exceptional promise and ability. My research ability has matured through my postdocs. At the University of Pennsylvania, I collaborated closely with neuroscientists and published ground-breaking neural models. At Brandeis, I have continued to develop my abilities as an independent mathematician and published promising new methods in fields such as coupled oscillators and molecular motor dynamics.

My research and teaching make for valuable, healthy contributions to an undergraduate institution. Virtually any undergraduate who learns calculus and a programming language will have the opportunity to take the lead in publishable research projects in math and biology. They will learn the principles of scientific thought, which will serve them well at \School~and beyond.

I am committed to providing high-quality, equal, and accessible education for all students, as evidenced by my teaching evaluations. My teaching portfolio boasts eight years of teaching at different levels (calculus sequence, differential equations, linear algebra, and discrete math). As a doctoral student, I was shortlisted for the \textbf{Elizabeth Baranger teaching award}, the most prestigious teaching award at the University of Pittsburgh. I strongly believe in the principle that learning is best accomplished with context and practice. My students do not learn in a vacuum, but instead learn concepts alongside the human triumph and defeat behind many concepts we take for granted today, such as matrix notation and Euclid's fifth postulate. Students at \School~will greatly benefit from this approach, and in turn, will drive me towards excellent instruction. I believe that students are best taught based on the needs of the individual and use numerous teaching styles to this end (including expeditionary learning, inquiry-based learning, and differentiated instruction).

Finally, I am a first-generation US Citizen who grew up all over the world  (including Swaziland, South Korea, and the Philippines), but by and large grew up in poverty in the United States. These environments exposed me to diverse cultures (including severe socio-economic disparities). While I have lived in the US since adolescence, this country is incredibly unique and I have continuously adjusted over the past several decades to fit into its culture. This experience, combined with my close friendships with people of diverse backgrounds, has helped me understand the difficulty of adjusting to a new life in the US while attending a competitive program. I believe that I could make valuable leadership contributions to diversity programs at \School.


As part of my application I include a curriculum vitae, teaching statement, and research statement. Please request additional details as needed, and I look forward to our correspondence.


\closing{Sincerely,}
\end{letter}
\end{document}